Query Optimization for Dynamic Imputation

### 2017-05-11 paper/algorithm.tex
fixing some wrong comments in algo section

The plan cache uses the partial order of plans defined by  $\langle \textsc{Dirty}, \textsc{Penalty}, \textsc{Time} \rangle$ to
collect sound and complete Pareto frontiers. For plans with the same dirty set, we can treat $\langle \textsc{Penalty}, \textsc{Time} \rangle$
as a total order, allowing us to appropriately select the frontier. Plans with different $\textsc{Dirty}$ sets cannot be compared. The final
Pareto frontier produced by the optimizer corresponds to the collection of plans associated with the empty dirty set.

@@

In order to support a large number of joins, with reasonable planning times, \ProjectName{} can maintain approximations of the Pareto sets,
rather than exact sets. To do so, dominated plans are still removed based on new non-dominated plans, but new plans are only added
if they are significantly different from any existing plan in the set. The distance between plans is determined based on the cost penalty and time
values associated with a plan.  Planning times are discussed further in \Cref{sec:results}.

>>>>

The plan cache uses the partial order of plans defined by  $\langle \textsc{Dirty}, \textsc{Penalty}, \textsc{Time} \rangle$ to
collect sound and complete Pareto frontiers. Plans with different $\textsc{Dirty}$ sets cannot be compared. The final
Pareto frontier produced by the optimizer corresponds to the collection of plans that best tradeoff imputation quality and
execution time.

@@

In order to support a large number of joins, with reasonable planning times, \ProjectName{} can maintain approximations of the Pareto sets. 
A non-dominated plan can be approximated by an existing plan in the set, if the distance between them is smaller than some predefined bound.
Approximated plans are not added to the frontier, pruning the search space further. 
Planning times across both exact and approximate Pareto frontiers are discussed further in \Cref{sec:results}.
